---
title: "Lego"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```
#Has lego used more colors over time
Combine inventory_parts and colors datasets
```{r}
names(colors)[1]<-"color_id"
inventory_parts_colors<-inventory_parts%>%
  merge(colors, by = "color_id")
```
Select year and id from sets
```{r}
set_year<-sets%>%
  select(set_num, year)
```
Select iventory id and set_num from inventory
```{r}
inventory_set<-inventories%>%
  select(id, set_num)

names(inventory_set)[1]<-"inventory_id"
```
Merge inventory_set and set_uyear
```{r}
inventory_set_year<-inventory_set%>%
  merge(set_year, by= "set_num")%>%
  select(inventory_id, year)
```
Combine color and year
```{r}
color_year<-inventory_parts_colors%>%
  merge(inventory_set_year, by = "inventory_id")%>%
  select(inventory_id, name, year)
```
Number of Colors per year
```{r}
color_year_final<-color_year%>%
  group_by(year)%>%
  mutate(color_number = n_distinct(name))

color_selected<-color_year_final%>%
  select(year, color_number)

color_final<-unique(color_selected)
```
Graph Colors Over Years
```{r}
legoplot<-ggplot(data = color_final, aes(year, color_number))+geom_col(fill = "darkblue")
legoplot+ggtitle("The Number of Colors Used By Lego From 1950-2018")+theme(plot.title = element_text(hjust = 0.5))
```
Summary Stats
```{r}
summary(color_final$color_number)
```
The Year with The Most Colors
```{r}
color_final%>%
  filter(color_number == 99.0)
```
Let's Look at The Number of Colors Per Theme 
```{r}
names(themes)[1]<-"theme_id"
sets_themes<-sets%>%
  merge(themes, by = "theme_id", all.x = TRUE)
theme_color<-sets_themes%>%
  merge(inventory_set, by = "set_num", all.x = TRUE)%>%
  merge(inventory_parts, by = "inventory_id", all.x = TRUE)%>%
  merge(colors, by = "color_id", all.x = TRUE)%>%
  select(c("year", "name.y", "name"))
  names(theme_color)[1:3]<-c("year", "theme", "color")
  
color_theme_final<-theme_color%>%
  group_by(theme)%>%
  mutate(color_number = n_distinct(color))

color_theme_final<-color_theme_final%>%
  select(c("theme", "color_number"))%>%
  unique()%>%
  filter(color_number>36)
```
Graph Number of Themes Per Color
```{r}
ggplot(data = color_theme_final, aes(theme, color_number))+geom_col(color = "darkblue")+theme(text = element_text(size=8),axis.text.x = element_text(angle=90, vjust=2))ggtitle("The Top 103 Themes With The Most Color")+theme(plot.title = element_text(hjust = 0.5))
```
Find out What Theme Has the Max Amount of Colors
```{r}
max(color_theme_final$color_number)
color_theme_final%>%group_by(color_number)%>%filter(color_number == 78)
```



